
# Reading in + cleaning the data:
The code below creates the following data frames to be used:

+ combined - eyepaths and orbpaths combined
+ left_tests - holds points for balls that go left
+ up_tests - holds points for balls that go up
+ down_tests - holds points for balls that go down

```{r, reading in the data}
library(ggplot2)
library(gganimate)
library(dplyr)
library(transformr)

eyepaths <- read.csv("all_eye_paths.csv")
orbpaths <- read.csv("all_orb_paths.csv")

eyepaths
orbpaths

## Directions:
# Left: 4,7,10,12,14
# Up: 1,5,9,11,15
# Down: 2,3,6,8,13 

# Combining orb paths and eye tracking
combined <- eyepaths %>%
  full_join(orbpaths, by = c("test","time"), suffix = c("_eye", "_orb")) %>%
  mutate(y_orb = as.double(y_orb))

combined

# Separating by direction 

left_tests <- combined %>%
  filter(test %in% c(4,7,10,12,14)) %>%
  mutate(test = as.factor(test)) %>%
  na.omit()

up_tests <- combined %>%
  filter(test %in% c(1,5,9,11,15)) %>%
  mutate(test = as.factor(test)) %>%
  na.omit()

down_tests <- combined %>%
  filter(test %in% c(2,3,6,8,13 )) %>%
  mutate(test = as.factor(test)) %>%
  na.omit()

left_tests # holds points for balls that go left
up_tests # holds points for balls that go up
down_tests # holds points for balls that go down

#write files
write.csv(left_tests, "C:\\Users\\joann\\OneDrive\\Desktop\\EMC\\EMC Analysis\\left-tests\\left_tests.csv", row.names = FALSE)
write.csv(up_tests, "C:\\Users\\joann\\OneDrive\\Desktop\\EMC\\EMC Analysis\\up-tests\\up_tests.csv", row.names = FALSE)
write.csv(down_tests, "C:\\Users\\joann\\OneDrive\\Desktop\\EMC\\EMC Analysis\\down-tests\\down_tests.csv", row.names = FALSE)
```

# Plotting the Data
The code below plots the x-component and y-component of one direction, both individually by test number and then altogether. You can change/copy the code and change "left_tests" to "up_tests" or "down_tests" to simulate other tests.

```{r, plotting}
# plots all test's x-comp
combined <- combined %>% na.omit()
ggplot(combined, aes(x = time, y = x_eye)) +
  geom_line(color = "red") +
  geom_line(aes(x = time, y = x_orb), color = "blue") +
  facet_wrap(~test)

# plots all test's y-comp
ggplot(combined, aes(x = time, y = y_eye)) +
  geom_line(color = "red") +
  geom_line(aes(x = time, y = y_orb), color = "blue") +
  facet_wrap(~test)


# X comp for left_tests
left_tests %>%
  ggplot(aes(x = time, y = x_eye)) + 
    geom_line(color = "red", linewidth = 1) +
    geom_line(aes(x = time, y = x_orb), color = "blue", linewidth = 1) + 
    scale_x_continuous(breaks = seq(0, 3200, by = 800)) +
    facet_wrap(~test)

left_tests %>%
  ggplot(aes(x = time, y = x_eye, color = test)) + 
    geom_line() +
    geom_line(aes(x = time, y = x_orb)) + 
    scale_x_continuous(breaks = seq(0, 3200, by = 800))

# Y comp for left_tests
left_tests %>%
  ggplot(aes(x = time, y = y_eye)) + 
    geom_line(color = "red", linewidth = 1) +
    geom_line(aes(x = time, y = y_orb), color = "blue", linewidth = 1) + 
    scale_x_continuous(breaks = seq(0, 3200, by = 800)) +
    facet_wrap(~test)

left_tests %>%
  ggplot(aes(x = time, y = y_eye, color = test)) + 
    geom_line() +
    geom_line(aes(x = time, y = y_orb)) + 
    scale_x_continuous(breaks = seq(0, 3200, by = 800))

## for graphing single tests y component...
combined %>% 
  filter(test == 11) %>%
  ggplot(aes(x = time, y = y_eye)) +
  geom_line(color = "red") +
  geom_line(aes(x = time, y = y_orb), color = "blue") +
  scale_x_continuous(breaks = seq(0, 3200, by = 800))
```

```{r}

```


# Animating Graphs by time
The following code is scuffed, but basically it takes in one of the directions, and the you need to filter to only pick one trial you want simulated, and then it plots that trial's x-component. You can also have it plot the y-component by copying the code and changing x_eye and x_orb to y_eye and y_orb respectively.

The animation will show up in the folder that this script is in, but as 100 individual frames. To turn these into a gif, use this website: https://ezgif.com/maker 

```{r, testing gganimate}
# data manipulation...
forAnim <- left_tests %>%
  filter(test == 4) %>%
  mutate(x_eye = x_eye + 3)

p <- ggplot(forAnim, aes(x = time, y = x_eye)) + 
  geom_line(color = "red") +
  geom_line(aes(x = time, y = x_orb), color = "blue") +
  transition_reveal(time)

print(p)
```